\section*{List of Major Changes}

Here we respond to the main comments, noting which reviews they come from.

\paragraph{M1.} We have better highlighted the motivation and scientific contributions of the work in Section 1.1 and demonstrated that how our work can lead to
a better understanding of the sleep quality in Section 4.2.4.

\paragraph{M2.} We have clarified the aim and better explained the results of our user survey, showing how \systemname can help users
improve their sleep behaviours (a question raised by all reviewers). This can be found at Section 4.2.4. The revision shows that
\systemname successfully helped some of our testing users in understanding the causes of poor sleeps. Specifically, our data reveal that
the hand position was the reason for frequent numb arms and nightmares for two of our participants, the sleeping posture and hand position
contributed to snoring for another participant, and the excessive light intensity and frequent noises of the environment led to bad sleeps
for a fourth participant. Based on these findings, we then suggested ways to improve their sleeping habits and a return visit of these
users shows that our suggestions helped to improve their sleep quality.

\paragraph{M3.} We now provide discussions on the use of a PSG in Sections 1 and 6 (a question raised by reviewers 1 and 4). See also R1.1.

\paragraph{M4.} Section 2.1 and Section 3.1 of the revised manuscript give further details on our experimental setup per reviewer feedback (raised by reviewers 1, 4 and 5). See also R1.2, R1.4, R4.4, R4.6, and R5.11.

\paragraph{M5.} We have updated Section 2.4 to include a detailed description of our Hidden Markov Model (HMM) model (raised by reviewers 1 and 4). See also R1.5.


\paragraph{M6.} We have provided a discussion on how to tackle multiple-sleeper scenarios, the occurrence of unusual arm positions, etc. This can be
found at Section 5.

\paragraph{M7.} We have made all the minor corrections suggested by the reviewers and some others.
