\section*{Reviewer 2}
\paragraph{R2.1} In addition to sleep stages, our work also focuses on tracking sleep behaviours (like hand positions and respiratory motions) and the sleeping
environment (like lighting and acoustic events). Our goal is to help a user to understand poor sleep but not quantify the sleep quality. We
do not compare to medical-grade equipment like PSG due to the scope of the work and for practical reasons. This is clarified in
Section 3.3. Please see also R4.1 and R1.1. Thanks for the feedback.


\paragraph{R2.2} Yes, \systemname is a sleep monitoring system for wearable devices. However, it can track a richer set of events,
including body postures, hand positions, body rollover counts, micro-body movements, acoustic events, and illumination conditions that are
not supported by Fitbit. We show that these rich events can help some of our users in understanding the causes of poor sleep and
subsequently to improve their sleep quality (see also M2). We have revised the introduction section to better highlight our contributions.
W thank the reviewer for the feedback.

\paragraph{R2.3} In terms of contributions to the community, Oour paper presents new algorithms to monitor and detect a range of sleep
activities on wearable devices. Many of these are not supported by Fitbit (see R2.2) , a state-of-the-art sleep monitoring system on
wearable devices. We also demonstrate that the tracked events can help users improve their sleep quality. We hope our work can encourage
more research on exploiting wearable sensors for health care.   This contribution is now highlighted in Section 4.2.4.
